---
title: "Robust_Regression"
author: "Rita M Ludwig"
date: "12/23/2018"
output: html_document
---
A R script that runs a robust regression, regressing scores on the Planfulness Scale on count of check-ins to the recreation center to test whether Planfulness moderates individual slopes of goal persistence over time.
```{r setup, include=FALSE}
##Required packages to run the script
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(MASS)) install.packages("MASS")

##Import data
data=read.csv("~/scales_and_count_clean_planfulnessREC.csv")
```
Run robust regression- iterative re-weighting least squares with Huber weights. Predict count of check-ins in winter term by Planfulness score.

```{r P predict Count}
fallactivity=filter(data,!str_detect(term,"winter")) %>%
  subset(., select= -c(term))

predictfall=rlm(fallactivity$Count ~ fallactivity$Planfulness_score)
summary(predictfall)

winteractivity=filter(data,!str_detect(term,"fall")) %>%
  subset(., select= -c(term))

predictwinter=MASS::rlm(winteractivity$Count ~ winteractivity$Planfulness_score)
summary(predictwinter)
```
Plot.
```{r plotting}
ggplot(data, aes(x=Planfulness_score, y=Count, color=term)) +
    xlab("Planfulness score") + ylab("Recreation center swipe-in count") +
    geom_point(aes(shape=term)) +
    scale_shape_manual(values=c(8, 19)) +
    scale_colour_grey() + theme_bw() + 
    geom_smooth(method=loess,   # Add loess lines
                se=FALSE)
```
